---
title: "Reddit STEP 2"
author: "Hunter Ratliff, @HunterRatliff1"
date: "7/15/2019"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)        # Silences most chunk outputs

## Ste time
# Sys.setenv(TZ="America/Chicago")    

suppressPackageStartupMessages(require(tidyverse))
require(ggthemes)
require(lubridate)
require(stringr)
require(ggrepel)
require(kableExtra)
require(visreg)
require(corrplot)
require(kableExtra)
require(gridExtra)
# library(rhandsontable)
require(shiny)

# Get data
reddit <- readr::read_csv("Step2CKSurvey.csv", na = c("", "NA", "#N/A")) 

## Ste time
# Sys.setenv(TZ="America/Chicago")   
reddit <- reddit %>%
  mutate(
    Date_StudyStart = mdy(Date_StudyStart),
    STEP2.date      = mdy(STEP2.date),
    UW_FirstPass    = UW_FirstPass/100
  ) %>% 
  rename(UW_FP=UW_FirstPass)
# reddit <- readr::read_rds("redditSTEP1.rds")
```

```{r}
fluidRow(
  column(3, inputPanel(
    checkboxGroupInput("modelVars", h3("Variables for model"), inline=F, width="100%",
                       selected = c("UW First pass"="UW_FP"),
                       choices = c("UWSA 1"="UW_1", "UWSA 2"="UW_2", 
                                   "UW First pass"="UW_FP", "Goal score"="Goal",
                                   "NBME #6"="NBME_6", "NBME #7"="NBME_7", 
                                   "NBME #8"="NBME_8"))
  )),
  column(9, inputPanel(
    numericInput("UW1", label="UWSA 1", value = NA),
    numericInput("UW2", label="UWSA 2", value = NA),
    numericInput("UWfp", label="UW First pass (%)", value = 72, min=1, max=100),
    numericInput("goal", label="Goal/target score", value = NA),
    numericInput("NBME6", label="NBME 6", value = NA),
    numericInput("NBME7", label="NBME 7", value = NA),
    numericInput("NBME8", label="NBME 8", value = NA)
  ))
)

renderUI({
  paste0("Using STEP2 = ", code(paste(input$modelVars, collapse=" + ")),
         " as input")
})

  
renderPrint({ 
  modelFormula <- as.formula(
    paste0("STEP2 ~ ", paste(input$modelVars, collapse=" + ")," - 1"))
  
  
  modelFormula
  })
# 
# as.formula(
#   paste0("STEP2 ~ ", paste(input$modelVars, collapse=" + ")," - 1"))


# fluidRow(column(3, verbatimTextOutput("value")))

```



# Sample linear models

```{r DefineFormula}
modelFormula <- "STEP2 ~ UW_1 +  UW_FP - 1"

## For testing how many results aren't blank
# nrow(filter(reddit, !is.na(UWSA2), !is.na(NBME17)))
```

Using the formula: <code> `r modelFormula` </code>

```{r DefineModel}
### Sample linear models
modelFormula <- as.formula(modelFormula)
lm2 <- lm(modelFormula, data = reddit) #define model
summary(lm2)
# coefficients(lm2)
# residuals(lm2)
# fitted(lm2)
```

## Predicted scores

This predicts our scores (based on the model above)

```{r PredictScoreTable}

inputScores <- data_frame(
  Person = c("Hunter", "Laura", "Wes", "Test"),
  UW_1   = c(260, NA, NA, 260),
  # UW_2   = c(NA, NA, NA, 260),
  UW_FP  = c(0.741, NA, NA, 0.741),
  # NBME_6 = c(NA, NA, NA, NA),
  # NBME_7 = c(NA, NA, NA, NA),
  # NBME_8 = c(NA, NA, NA, NA),
  Goal   = c(260, NA, NA, NA)
)

inputScores <- inputScores %>%
  bind_cols() %>%
  data.frame(
    predict(lm2, inputScores, interval = "prediction", level=.95)
  )
inputScores %>% 
  mutate(
    fit = round(fit),
    lwr = round(lwr),
    upr = round(upr)
  ) %>%
  rename(`Fitted score`=fit, `Lower 95% CI`=lwr, `Upper 95% CI`=upr) %>%
  knitr::kable(caption = "Predicted scores")    
```

## Validate model








## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```




